Red-Giant Hot Jupiters: Brilliant Radio Emitter?

### 2015-04-20 ms.tex
Discussion about the radio brightness of giants are added

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
%\usepackage{lscape}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}
\usepackage{color}

@@

\affil{$^2$Research \& Development, Sum Labs,
  New York, NY  10001}

@@

On the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/3}  \\
&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp}
\end{eqnarray}
%%%
In order to compare the canonical hot jupiters and red giant hot jupiters, equation (\ref{eq:Pkinp}) can be re-normalized as 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
\end{eqnarray}
%%%
\memoYF{what is the typical wind velocity of AGB stars?}
Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as typical hot Jupiters. In other words, we could search for radio signal from these stars in $(\sqrt{50})^3 = 353$ times as large volume as the canonical hot jupiters.

@@

Using the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, radio emission of planetary companions with varying mass and orbital distance can be estimated. 
Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs at 100 pc in the plane of companion mass and orbital distance, as well as their cyclotron frequency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
 \begin{minipage}{0.5\hsize}
  \begin{center}
   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8.eps}
  \end{center}
 \end{minipage}
 \begin{minipage}{0.5\hsize}
  \begin{center}
   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5.eps}
  \end{center} 
 \end{minipage}
   \caption{Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc. The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere. The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion. Bottom panel: cyclotron frequency, i.e., the frequency of radio emission. }
  \label{fig:two}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

(Jason)

>>>>

\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{natbib}
%\usepackage{lscape}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{array}
\usepackage{appendix}
\usepackage{comment}
\usepackage[dvipdfmx]{color}
%\usepackage[dvipdfmx]{graphicx}

@@

\affil{$^2$Research \& Development, Project Florida Labs,
  New York, NY  10001}

@@

On the assumption that the radio emission is proportional to the input kinetic energy (equation (\ref{eq:Pinp_kin})), the scaling of the radio emission is expanded as follows: 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} &=& nv^3 r_s^2 = n v^3 \left( \frac{\mu_0^2 \mathcal{M}^2}{8\pi^3 m_{\rm p}nv^2} \right)^{1/3}  \\
&=& P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp}
\end{eqnarray}
%%%
In order to compare the canonical hot jupiters and red giant hot jupiters, equation (\ref{eq:Pkinp}) can be re-normalized as 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
&\approx & 490 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \label{eq:Pkinp} \\
\end{eqnarray}
%%%
\memoYF{what is the typical wind velocity of AGB stars?}
Therefore, the jupiters to the AGB stars are intrinsically 50 times as bright as canonical hot Jupiters. In other words, we could search for radio signal from these stars in $(\sqrt{50})^3 = 353$ times as large volume as the canonical hot jupiters.

@@

Using the scaling relation of magnetic moment described in \S\ref{ss:magneticfield}, radio emission of planetary companions with varying mass and orbital distance can be estimated. 
Figure \ref{fig:radio} shows the intensity of radio emission from RGHJs at 10~pc in the plane of companion mass and orbital distance, as well as their cyclotron frequency.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[bp]
 \begin{minipage}{0.5\hsize}
  \begin{center}
   \includegraphics[width=\hsize]{radio_emission_Mdot1e-8.eps}
  \end{center}
 \end{minipage}
 \begin{minipage}{0.5\hsize}
  \begin{center}
   \includegraphics[width=\hsize]{radio_emission_Mdot1e-5.eps}
  \end{center} 
 \end{minipage}
   \caption{Top panel: Intensity of radio emission (in the unit of Jy) from a companion to a RG star (left) and an AGB star at 1 pc. The hashed region with vertical lines are not observable because of the plasma frequency cut-off of Earth's ionosphere. The hashed region with horizontal lines are not observable because of the plasma frequency cut-off of the stellar wind plasma in the vicinity of the companion. Bottom panel: cyclotron frequency, i.e., the frequency of radio emission. }
  \label{fig:radio}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

(Jason?)

In the radio range, the brightness source of the radio emission is Rayleigh-Jeans tail of the Planck function, i.e., $S_{\nu } = 2kT\nu^2/c^2$. Recent observations revealed that this dependence on $\nu$ ($f \propto \nu^{\alpha }$ where $\alpha $ is 2) can approximately be extended as low frequency as 1 GHz \citet{gorman2013}, presumably as a result of the wavelength dependence of the opacity (at longer wavelength we see the region further from the center of the stars) and the decreased temperature as the distance from the stars increases. 
In this paper, we simply assume that the radio emission from the red giants themselves are approximated as a black body radiation. Therefore, the flux from the giants are:
%%%
\begin{eqnarray}
f_{\star } (\nu ) &=& \frac{2R_{\star }^2 k_B T \nu^2}{c^2 d^2}  \\
&\approx & 1.4 \times 10^{-9} ~\mbox{Jy} \left( \frac{d}{100 ~\mbox{pc}} \right)^{-2} \\
&& \times \left( \frac{R_{\star }}{10 R_{\odot }} \right)^2 \left( \frac{T_{\star }}{10^{4}~\mbox{K}} \right) \left( \frac{\nu}{1 ~\mbox{GHz}} \right)^2 
\end{eqnarray}
%%%
Therefore, for stars with $R_{\star } < 50 R_{\odot}$, companions around the stars are typically brighter than their hosts.
